Symmetric Peer-to-Peer Applications

### 2022-08-22 tpd-22.tex
...

The middleware expects to take full control of the application execution in
order to control its timeline, and also communicate events in the network.
For this reason, the basic API is to call an \code{init} function passing a
set of callbacks, which the middleware uses to communicate with the
application, and then call \code{loop} to yield control to the middleware:

{\footnotesize
\begin{verbatim}
int main (void) {
    ...  // initialize the UI
    p2p_init(1, 50, sizeof(G), &G, cb_sim, cb_eff, cb_rec);
    p2p_link("182.168.0.2", 5000, 2);
    p2p_loop();
    p2p_quit();
    ...  // finalize the UI
}
\end{verbatim}
}

>>>>

The middleware expects to take full control of the application execution in
order to control its timeline, and also to communicate events in the network.
For this reason, the basic programming API is to call a \code{loop} function
passing a set of callbacks, which the middleware uses to communicate with the
application:

{\footnotesize
\begin{verbatim}
int main (void) {
    p2p_loop (
        1,              // peer identifier
        50,             // simulation FPS
        sizeof(G), &G,  // pre-allocated full state
        cb_ini,         // init/quit callback
        cb_sim,         // simulation callback
        cb_ren,         // rendering callback
        cb_evt          // event triggering callback
    );
}
\end{verbatim}
}

The middleware assumes that each peer is assigned a unique identifier in a
contiguous range.
The FPS must be the same in all peers to ensure that the simulation executes
exactly the same.
The variable \code{G} must hold the full application state.
If dynamic allocation is required, it is necessary to hold a finite memory
pool in \code{G} with a custom allocator.
For instance, the moving rectangle application only requires to hold the
current position and direction:

{\footnotesize
\begin{verbatim}
struct {
    int x,  y;   // position
    int dx, dy;  // direction speed
} G;
int main (void) { ... }
\end{verbatim}
}

The middleware calls \code{cb\_ini} twice: at the beginning and at the end of
the loop.
It should be used to initialize (and finalize) the network topology, as well
as static globals that live outside the simulation memory, such as the window
and image textures.

{\footnotesize
\begin{verbatim}
void cb_ini (int ini) {
    if (ini) {
        // create the window
        // open arrow images
        // create peer links (peer-id, ip, port)
        p2p_link(2, "192.168.1.2", 5000);
    } else {
        // create the window
        // open arrow images
        // destroy a peer links
        p2p_unlink(2);
    }
}
\end{verbatim}
}

The middleware calls \code{cb\_sim} on every frame to affect the simulation
state \code{G} deterministically.
The callback must never perform any side effects, such as rendering the frame.
The calls normally happen during real-time simulation, i.e., while the user is
interacting with the application.
However, if the peer is out of sync, the middleware may ``time travel'' and
call the simulation many times to go back and forth and catch up with real
time.
This is the reason why \code{cb\_sim} should

This is why it is important that the simulation is detached from the view.

\subsection{The Time Machine}
\label{sec.tml.time}

at the same time as the user
is interacting with the application

twice: at the beginning and at the end of
the loop.
It should be used to initialize (and finalize) the network topology, as well
as static globals that live outside the simulation memory, such as the window
and image textures.

The core of the API are the 4 callbacks

The network topology is dynamic

%\item Peers have contiguous numeric unique identifiers.
